---
title: "CV"
name: Anamaria
surname: Elek
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::markdowncv: 
    theme: kjhealy
position: PhD Student
address: Working on comparative genomics and gene regulation.  
phone: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(data.table)
library(tibble)
library(dplyr)
library(rcrossref)
library(fontawesome)
my_orcid <- "0000-0002-3938-2494"
```

## Contact

`r fa(name = "map-marker-alt", fill = "steelblue")` Carrer del Bruc 107, 08009 Barcelona, Spain  

`r fa(name = "phone", fill = "steelblue")` +34 671 743 750  

`r fa(name = "envelope", fill = "steelblue")` anamariaelek@gmail.com  

[`r fa(name = "linkedin", fill = "steelblue")`](https://www.linkedin.com/in/anamaria-elek/) | 
[`r fa(name = "github", fill = "steelblue")`](https://github.com/anamariaelek) | 
[`r fa(name = "twitter", fill = "steelblue")`](https://twitter.com/anamariaelek)

## Experience

```{r}
tribble(
  ~ Where, ~ Position, ~ Year, ~ Institution, ~ Why,
  "Barcelona, ES", "PhD Student", "2019 - 2024", "Centre for Genomic Regulation", 
  c("PhD student in Comparative regulatory genomics group (Sebé-Pedrós lab)", 
    "Modeling cell type evolution using single-cell and chromatin profiling approaches"),
  "London, UK", "Bioinformatician", "2019", "The Institute of Cancer Research", 
  c("Bioinformatician in Genomics Facility", 
    "Development and maintenance of computational pipelines for the analysis of next-generation sequencing data."),
  "Zagreb, HR", "Intern", "2018", "Exaltum",
  "Implementing pipeline for the analysis of whole-genome and exome sequencing, and generation of personalized reports.",
  "Rouen, FR", "Intern", "2018", "omicX", 
  "Data visualizations for benchmarking of different biological analysis pipelines.",
) %>% 
  detailed_entries(Institution, Year, Where, Position, Why)
```

## Education

```{r}
orcid_edu_list <- rorcid::orcid_educations(my_orcid)[[my_orcid]][["affiliation-group"]][["summaries"]]
orcid_edu <- rbindlist(
  lapply(orcid_edu_list, function(x) as.data.table(x)),
  use.names = TRUE, fill = TRUE
)
orcid_edu[is.na(`education-summary.end-date.year.value`),`education-summary.end-date.year.value`:="present"]
orcid_edu[, details := list(
  "Project: Modeling cell type evolution using single-cell and chromatin profiling approaches",
  "Thesis: coRdon: an R package for codon usage analysis and prediction of gene expressivity",
  "Thesis: Structure and dynamics of the spliceosome"
)]
orcid_edu %>%
  detailed_entries(
    `education-summary.organization.name`,
    glue::glue("{`education-summary.start-date.year.value`} - {`education-summary.end-date.year.value`}"),
    glue::glue("{`education-summary.organization.address.city`}, {`education-summary.organization.address.country`}"),
    `education-summary.role-title`,
    details
  )

```

## Publications

```{r}
orcid_bib <- rorcid::orcid_citations(my_orcid)[,"citation"]
# add stupid package manually
orcid_bib <- orcid_bib[!grepl("cordon", orcid_bib$citation, ignore.case = TRUE),]
orcid_bib <- rbind(orcid_bib, c(
  "@article{Elek_2021, doi = {10.18129/B9.BIOC.CORDON}, url = {https://doi.org/10.18129/b9.bioc.cordon}, author = {Elek, A. and Kuzman, M. and Vlahovicek, K.}, title = {coRdon: codon usage analysis and prediction of gene expressivity}, journal = {R package}, publisher = {Bioconductor}, year = {2018}} "
))
write.table(orcid_bib,"orcid.bib")
bibliography_entries("orcid.bib") %>%
  arrange(desc(as.integer(stringr::str_extract(id,'\\d{4}$'))))

```

## Skills

`r fa(name = "python", fill = "steelblue")` Python |
`r fa(name = "r-project", fill = "steelblue")` R programming | 
`r fa(name = "linux", fill = "steelblue")` Linux/BASH |
`r fa(name = "server", fill = "steelblue")` HPC computing |
`r fa(name = "git-square", fill = "steelblue")` Git versioning |
`r fa(name = "docker", fill = "steelblue")` Docker


## Awards

```{r}
data.table(
  place = "EMBO | EMBL Symposium: The Identity and Evolution of Cell Types",
  date = "2021",
  location = "virtual",
  award = "Best poster award"
) %>% detailed_entries(place, date, location, award)
```

## Volunteering

```{r}
tribble(
  ~ date, ~ activity, ~ what, ~ type, ~ details,
  "2020 - 2022", "NGSchool", "bioinformatics summer school", "educational", 
  c("I have been working on scientific program and participants selection for the summer school.",
    "I was the speaker of two webinars (on R programming and single cell RNA-seq)",
    "and the mentor of a hackathon team of 10 people (working on RNA-seq analysis project).",
    "I was also leading the project of developing an NGSchool website (https://ngschool.eu/)."),
  "2021", "Introduction to Machine Learning", "CRG Internal Training Course", "educational", 
  c("I held a lecture and a workshop on feature selection and dimensionality reduction")
) %>% detailed_entries(what, date, type, activity, details)
```

## Training

```{r}
tribble(
  ~ date, ~ activity, ~ what, ~ where,
  "2018", "NGSchool: Nanopore sequencing & personalised medicine", "bioinformatics summer school", "Lublin, PL",
  "2017", "VBC Summer School", "molecular biology summer school", "Vienna, AT" 
) %>% detailed_entries(what, date, where, activity)
```



